Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-09-06 Latex_files/Thesis/chapters/chapter 1/main.tex
updates 06/09/2024

@@

\subsection{Literature related to laser induced nucleation}
From as early as 1996 it has been known that laser irradiation is a viable
method of inducing nucleation within a supersaturated solution \cite{Garetz1996}, 
the first reported case was notable as it used a 1.064 $\mu m$ laser meaning 
it was unlikely to be a photo-chemical reaction but rather a physical one. 
Future research has found nucleation can be induced by 1 of 3 routes involving 
direct laser induction: firstly, Non-photochemical laser induced nucleation 
(NPLIN) where the solution is irradiated with a pulsed laser \cite{Garetz1996,
Garetz2002,Sun2006}, several papers have debated the exact mechanism that 
induces NPLIN \cite{Garetz2002, Knott2011}. Two suggested hypothesis are: 
an optical Kerr effect, where the solute molecules are aligned to lower the 
nucleation barrier \cite{Knott2011}; a dielectric polarisation effect, in 
which solute clusters are stabilised within the electric field which drastically 
increases the likelihood of nucleation\cite{Alexander2008}. Both hypothesise 
have their limitations and there has yet to be a single theory that explains 
NLPIN thoroughly. In either case the mean pulse intensity needs to be kept 
relatively low (on the order of $0.1-0.01 GW/cm^2$), as high intensity pulses 
lead to a completely different nucleation mechanism.

High intensity laser induced nucleation (HILIN), where the pulse intensity 
is on the order of several $PW/cm^2$ is far simpler a mechanism to explain 
in comparison to NPLIN. The production of nuclei can be wholly associated 
to a cavitation process within the target solution, where the laser focus 
results in thermo-cavitation and the subsequent pressure change leads to
a nucleation event around the focus of the laser \textcolor{red}{[ , , ]}. 
There is still not a general consensus on how cavitation influences the 
local supersaturation \textcolor{red}{[ , ]}, nor is there a clear 
understanding of what properties of the crystal can be controlled 
\textcolor{red}{[ , ]}. It has been suggested that in theory any solution 
can undergo HILIN \textcolor{red}{[ ]}, proving such a theory requires a 
strong understanding of the phenomena both before and after cavitation 
occurs.

Lastly, there is trapping induced nucleation, this is where optical tweezers 
come into play, the optical trap has been shown to have different effects 
on supersaturated solutions depending on where it has been focused. When 
focusing on the cover slip, supersaturated solutions of glycine and $D_2O$ 
were shown to create a dense liquid droplet of glycine and water 
\textcolor{red}{[ , ]}, applying DLS analysis showed that the dense liquid 
region was populated by clusters that would consolidate together upon being 
focused by the optical trap \textcolor{red}{[ ]}. Molecular simulations of 
glycine solutions showed that these clusters are unstable when using pure 
glycine below the saturation point \textcolor{red}{[ ]} suggesting that the 
clusters are formed due to glycine reaction products. When the optical trap 
was moved from the cover slip to the air-solution interface nucleation would 
occur before a dense liquid region could form \textcolor{red}{[ ]}. Repeated 
experiments where the laser is focused on the air-solution interface have 
lead to a variety of different nucleation events. In some instances the 
nucleation occurs spontaneously after a short period of time \textcolor{red}{[ ]}; 
whereas allowing a solution to age results in the formation of amorphous 
precursors that when irradiated will nucleate immediately \textcolor{red}{[ ]}. 
The precursors are only seen when the solution is irradiated by an optical tweezer 
and the growth rate can be controlled somewhat by varying the laser power 
\textcolor{red}{[ ]}. Notably the only work has been done with simply 
irradiating the solution with a trapping potential, there has not been an 
attempt to introduce a trappable object into the solution, the trapping 
potential has been used to influence the growth of a crystal front 
\textcolor{red}{[ ]}.

\subsection{Optical Torque}
For any electromagnetic field it is possible to transfer both linear and 
angular momentum \cite{Beth1936MechanicalDA}; more accurately the field 
is said to have both orbital and spin momentum. Though there is some 
debate on how to decompose the total momentum into these two components 
\cite{Bruce2020, Svak2018}, for this thesis we do not need to calculate 
the exact quantities and will instead look at the broader effects of both 
components. Orbital angular momentum arises from the shape of the wavefront 
of the particular field in question; for simple Gaussian beams the wavefronts 
are uniform and equally spaced resulting in the typical radiation pressure 
that Ashkin and co demonstrated \cite{Ashkin1980}. However, higher order 
modes of a Gaussian beam (for example: Laguerre-Gaussian modes) have 
non-uniform wave fronts meaning the orbital momentum has both angular and
linear components; depending on the relative size of the target particle 
one can induce rotation, or orbiting \cite{Bruce2020, Courtial2000}.

Spin angular momentum (SAM) is attributed to the spin density of the field, 
early research has shown that the spin density is non-zero for any beam despite
the fact that the total SAM transferred to a medium is 0 \cite{Svak2018, 
Bliokh2014}. This has sparked debate if SAM is even a physical quantity as 
it does not aid in the transport of energy directly \cite{Bliokh2014} and 
so cannot be directly observed in some cases despite being non-zero. This 
paradox is resolved by representing the wave as an array of spin momentum 
loops that all together cancel one-another out when the medium is homogeneous.
Spacial inhomogeneities cause these spin loops to non longer be equal, resulting
in non-zero spin density, anisotropic mediums (such as birefringent crystal 
lattices) experience a transfer of spin angular momentum allowing for optical
torque transfer. It has even been shown that in the case of homogeneous spheres, 
the spin component of a focused beam can result in additional orbital angular
momentum via spin-to-orbital conversion \cite{Yevick2017}.

Birefringence is a material property often seen in crystalline materials, 
if the crystal lattice has a different structures when viewed at different 
orientations then light will be refracted differently depending on its 
polarisation. For circularly polarised light the inhomogeneity results in 
a high degree of SAM being transferred to the target object \cite{Parkin2009,
Arita2016}, this has been exploited to rotate microspheres as fast as 1000 Hz 
while suspended in a bulk medium \cite{Arita2016} as well as a means of 
measuring the local temperature and shear response of said medium 
\cite{Millen2014, RodriguezSevilla2018}. Calculating the optical torque 
applied to a birefringent material is given via:

\begin{equation}
	\label{eq:opt_torque}
	\begin{aligned}
		\tau_{opt} =& -\frac{\epsilon}{2\omega_{laser}}E_0^2sin(kd(\Delta n))cos2\theta sin2\phi \\ &+  \frac{\epsilon}{2\omega_{laser}}E_0^2 (1-cos(kd(\Delta n))sin2\phi)
	\end{aligned}
\end{equation}

Where $\theta$ is the angle between the particle's long axis and the Poynting
vector of the local EM field, and $\phi$ is the phase shift in the EM field.  
The first term represents the 'orientational' torque which is due to the target 
particle being aligned along the EM field, when aligned $\theta=0$ meaning 
the entire term is negligible for particle's with a stable orientation. The 
second term is due purely to the polarisation of the optical trap, for 
circularly polarised light $\phi=\pi/4$ thus maximising the torque transferred 
to the target particle. Birefringence can also be induced if the target 
particle has an anisotropic shape, in particular if the particle shape is 
elongated along one major axis; the go to particle shape is a silica dimer 
(two spheres tangentially attached) due to silica's stability and strong 
adhesion. Using a silica dimer research groups have achieved a rotation 
frequency in the realm of several GHz \cite{Ahn2018} in a vacuum.

\section{Shear induced Nucleation}
It has long been known that fluid shear rate plays a role in influencing
nucleation; however, the exact relationship between shear rate and nucleation
rate has only been recently understood for specific solutions. Theoretical research 
into shear induced nucleation suggests that there should be a slight increase 
in the nucleation rate at low shear rates, reaching a maximum increase in 
nucleation rate, and then at higher shear rates the nucleation rate begins 
to drop off. This has been shown theoretically for both simple colloidal
\cite{Mura2016,Debuysschere2023,Richard2015} and ice crystal formation 
\cite{Goswami2020}; however, no experimental work into these systems has 
been conducted to prove this is the case.  There is some experimental 
evidence for this phenomena in simple salt and protein solutions - though 
the authors emphasise that mechanical agitation cannot be ruled out - 
there has not been a exhaustive study into the shearing effects apart from 
in glycine solutions. In \cite{Debuysschere2023} it was found that a shear 
rate of around $3000\ s^{-1}$ was the maximum shear rate that would yield 
the highest nucleation rate. Using the theoretical model established in 
\cite{Mura2016,2001} which modifies the CNT to account for the effects of 
a nucleus undergoing shearing, accounting for the fact that a nucleus' 
growth is undergoing competition between flow-mediated molecular transport 
and the strain applied by the flow field which inhibits the growth of the 
nucleus. There central conclusion (from both the theoretical and experimental 
results) is that there is an optimal shear rate in which the nucleation 
rate is maximised. However, a question that arises from this result, if 
there is a optimal shear rate in which molecular transport is maximised 
and strain is minimised, then surely there should also be a shear rate 
in which the molecular transport and strain are equal - allowing one to 
suspend a nucleus at a constant radius. In this scenario, the molecular 
transport would prevent the nucleus from dissolving, but the strain would 
prevent the nucleus from growing. This however would require one to be 
able to apply a continuous shear rate to a targeted nucleus with high 
precision, there is also no model for an individual nucleus undergoing growth.

\section{Aims and Objectives}
Overall the aim of the PhD is to study viability of using micro-rotors to
generate localised fluid flow around the beam focus. The results are reported
in chapter 3, this is then succeeded by experimental work where we 
instead using a galvano-mirror to generate shear flow. While overall unsuccessful
the addition of a moving beam focus showed that the growth of a nucleus can be localised around the trap focus.

In addition, computer simulations studying the dynamics of asymmetric dimers 
and their applications as complex micro-rotors are discussed in chapter 4. 
Lastly two novel methods of measuring rotational motion are discussed in 
chapter 5; firstly via a novel detection fibre method that allows for 
instantaneous measurements of the orientational behaviour of optically 
trapped ellipsoids/dimers; and secondly we create a simulative quadrant 
photo diode that replicates laboratory results, utilising linear regression 
techniques we measure the change in orientation in order to measure the 
optical torque applied to a non-birefringent particle.

>>>>

\subsection{Anti-solvent Crystallisation} 
Anti-solvent crystallisation is a more involved separation method ,
by adding a new solvent that is miscible with the old solvent but is 
immiscible with the solute, the solute's effective solubility is decreased.
As such, the solution becomes supersaturated. This has the trade off in that the overall mass ratio between the solvent and solute is now lower. Careful
measurement of the anti-solvent is required in order to ensure that the 
decrease in solubility is not out matched by the decrease in mass ratio.
Anti-solvent crystallisation is not as common due to the fact that not all
solutions will have an ideal anti-solvent candidate.

@@

\subsection{Gaussian Beams}
A Gaussian Beam is a simplistic approximation of a laser beam, in short
it is an unbounded plane wave whose intensity of the electromagnetic 
field falls off from the centre similar to a normal distribution. This 
is perfectly fine for beams with a divergence angle of $0^{\circ}$, but 
later studies into focused beams has shown that the assumption of a 
Gaussian intensity profile is inaccurate. A study conducted by Lock and Gouesbet found that as the Gaussian beam was focused the fall off in 
the electric field would consequentially induce additional electromagnetic fields \cite{Lock1994}. As a result the shape of the beam profile diverges from a Gaussian profile for focused beams. Regardless, for optical trapping experiments it is useful to approximate a Gaussian beam as many descriptions
of lasers are simply combinations of plane waves (with varying amplitudes
and wave vectors). More information on electromagnetic theory is covered in 
chapter 2 but for now any mention of a focused laser can be thought of as a
Gaussian beam, unless specified otherwise.

\subsection{Literature related to laser induced nucleation}
From as early as 1996 it has been known that laser irradiation is a viable
method of inducing nucleation within a supersaturated solution
\cite{Garetz1996}. The first reported case was notable as it used a 
1.064 $\mu m$ laser, the glycine solutions would appear transparent to
such a laser which would suggest there was no photo-chemical reaction.
Later studies into this phenomena found that the laser polarisation 
can influence the polymorph produced. With circularly polarised light 
producing $\alpha$-glycine and linearly polarised light forming
$\gamma$-glycine \cite{Garetz2002}. Future research has found nucleation 
can be induced by 1 of 3 routes.

\subsubsection{Non-Photochemical Laser Induced Nucleation}
Non-photochemical laser induced nucleation (NPLIN) involves irradiating 
a solution with a pulsed laser \cite{Garetz1996,Garetz2002,Sun2006}. 
The laser itself does not have to be heavily focused, instead irradiating
a large region of the solution all at once. The choice of laser is of
particular importance; with nucleation probability changing depending 
on the wavelength \cite{Kacker2017}. In addition, the choice of solute will effect the setup, not only because some solute's are unaffected, but also because there is a minimum laser threshold before nucleation is observed 
\cite{Garetz2002}. Several papers have debated the exact mechanism that 
induces NPLIN \cite{Garetz2002, Knott2011}. A suggested theory to this is 
an optical Kerr effect, for anisotropically charged solute molecules the 
electric field can reorient them to match the propagation direction 
\cite{Garetz2002}. If enough molecules are co-aligned the free energy 
barrier is reduced to allow for ambient nucleation \cite{Knott2011}. 
An alternative theory is the dielectric polarisation effect, in 
conditions that are unfavourable to cluster formation the polarising 
effect can stabilise the clusters \cite{Alexander2008}. As the cluster  concentration rises so does the likelihood of nucleation \cite{Vekilov2010}. 
Both theories are similar to one another but where the optical Kerr theory
is limited to anisotropic solute molecules, the direct polarisation 
theory is more flexible. Regardless both theories struggle to explain
why the phenomena is not observed in all nucleation systems 
\cite{Korede2023}, such as acetamide which is similar to urea which 
does nucleate when irradiated \cite{Ward2016}. One of the benefits of 
NPLIN is that since the pulses are relatively low in their intensity 
they can be fired off quickly in succession, allowing for continuos 
crystallisation set ups. Overall, the NPLIN phenomena needs further 
research to properly describe its effects. The mean pulse intensity 
needs to be kept relatively low (on the order of $0.1-0.01 GW/cm^2$), 
as high intensity pulses lead to a completely different nucleation 
mechanism.

\subsubsection{High Intensity Laser Induced Nucleation}
High intensity laser induced nucleation (HILIN), where the pulse intensity 
is on the order of several $PW/cm^2$ is far simpler a mechanism to explain 
in comparison to NPLIN. The production of nuclei can be wholly associated 
to a cavitation process within the target solution, where the laser focus 
results in thermo-cavitation and the subsequent pressure wave leads to
a nucleation event around the focus of the laser \cite{Yoshikawa2005, 
Soare2011, Barber2019}. What remains in question is both how the physical 
properties (size, polymorph, etc) are influenced by the cavitation process, 
and how the pressure change triggers nucleation. The former has already 
been investigated; by adjusting the focal position Ikeda \textit{et al} 
could control the polymorph of indomethacin \cite{Ikeda2015}, this is not 
a universal method however, as it has also been shown that laser power can 
influence the crystal polymorph \cite{Wang2010}. The latter is a tricky 
task to address due to the fact that these cavitation bubbles form and collapse in less than $100\ \mu s$. Using fluorescence dyed proteins, researchers were able to observe a sudden spike in fluorescence just 
as the cavitation bubble began to collapse, they suggested that due 
to the collapse of the cavitation bubble the protein clusters are brought together at the lasers focal point. However, while the fluorescence 
imaging indicates a local concentration increase it is difficult to 
quantify this change depending on the size of the bubble \cite{Korede2023}. It
has been suggested that in theory any solution can undergo HILIN \cite{Korede2023}, but proving such a theory requires a clear 
understanding of the phenomena both before and after cavitation occurs. Current research aims to combine experimental research with computer 
simulations to develop a universal theory, with the hope that this could 
also be related to NPLIN.

\subsubsection{Trapping Induced Nucleation}
Lastly, there is trapping induced nucleation, this is where optical tweezers 
come into play. Due to the radiation pressure created by the focused beam,
it is possible to manipulate the solute, this was demonstrated with amino
acids such as glycine \cite{Tsuboi2009}. Whether or not a crystal forms is 
due to the location of the laser focus. When focusing on the cover slip, supersaturated solutions of glycine and $D_2O$ were shown to create a dense liquid droplet of glycine and water \cite{Yuyama2010, Yuyama2012}. The dipole moment of the glycine molecules is too small to be influenced by the optical trap, as such it would suggest that larger aggregates are being manipulated. Applying DLS analysis to the dense liquid region showed that it was populated by clusters that would consolidate together upon being focused by the 
optical trap \cite{Gowayed2021}. Molecular simulations of glycine solutions showed that these clusters are unstable when using pure glycine below the saturation point suggesting that the clusters are formed due to glycine reaction products \cite{Sweatman2022}. When the optical trap is moved from the cover slip to the air-solution interface, nucleation would occur before a dense liquid region could form \cite{Yuyama2010}.
Repeated experiments where the laser is focused on the air-solution interface have lead to a variety of different nucleation events. In some instances the nucleation occurs spontaneously after a short period of time \cite{Yuyama2010}. Whereas allowing a solution to age results in the formation of amorphous precursors that when irradiated will nucleate immediately \cite{Liao2022}. The precursors are only seen when the solution is irradiated by an optical tweezer and the growth rate can be controlled somewhat by varying the laser power \cite{Liao2022}. The reason why nucleation is only seen at the air-solution interface is due to the limited molecular mobility close to the interface. Often tweezing experiments will use a hydrophilic 
coating to minimise the height of the solution droplet and further limit
the molecular mobility \cite{Yuyama2012, Gowayed2021}.

Walton and Wynne discussed a plausible model for how the tweezer focus
could result in a nucleation event. Put simply, when the laser is focused
at the solution the radiation pressure draws in solute material, creating 
a concentrated region of solute. This also creates a depleted region 
around the focus and raises the local temperature. When the laser is 
turned off the depleted region around the focus quickly cools back to the 
ambient temperature. This sudden cooling allows for nucleation to occur
just outside the focus.

Laser induced nucleation has the potential to be a viable method for 
\textit{in-situ} studying of nucleation events. Using high numerical 
aperture lenses one can localise the nucleation event to a specific 
region of the solution. The current issue is that the mechanism behind
laser induced nucleation is not fully understood, as such it is rather
difficult to modify the laser for different solution parameters. Instead
it may be more effective to manipulate the solution using trapped particles.
An common method is by apply a torque to a trapped particle, creating 
a micro-rotor that can can generate fluid flow.

\subsection{Optical Torque}
It has long been known that electromagnetic fields can transfer linear and
angular momentum \cite{Beth1936MechanicalDA}; more accurately the field 
is said to have both orbital and spin momentum. Though there is some 
debate on how to decompose the total momentum into these two components 
\cite{Bruce2020, Svak2018}, for this project we do not need to calculate 
the exact quantities and will instead look at the broader effects of both 
components. Orbital angular momentum arises from the shape of the wavefront 
of the particular field in question; for simple Gaussian beams the wavefronts 
are uniform and equally spaced resulting in the typical radiation pressure 
that Ashkin and co demonstrated \cite{Ashkin1980}. However, higher order 
modes of a Gaussian beam (for example: Laguerre-Gaussian modes) have 
non-uniform wave fronts meaning the orbital momentum has both angular and
linear components; depending on the relative size of the target particle 
one can induce rotation, or orbiting \cite{Bruce2020, Courtial2000}.

Spin angular momentum (SAM) is attributed to the spin density of the field, 
early research has shown that the spin density is non-zero for any beam despite
the fact that the total SAM transferred to a medium is 0 \cite{Svak2018, 
Bliokh2014}. This has sparked debate if SAM is even a physical quantity as 
it does not aid in the transport of energy directly \cite{Bliokh2014} and 
so cannot be directly observed in some cases despite being non-zero. This 
paradox is resolved by representing the wave as an array of spin momentum 
loops that all together cancel one-another out when the medium is homogeneous.
Spacial inhomogeneities cause these spin loops to no longer be equal, resulting
in non-zero spin density, anisotropic mediums (such as birefringent crystal 
lattices) experience a transfer of spin angular momentum, imparting an optical
torque.

Birefringence is a material property often seen in crystalline materials, 
if the crystal lattice has different refractive indices for varying 
polarisations of light. For circularly polarised light this inhomogeneity 
results in a high degree of SAM being transferred to the target object \cite{Parkin2009, Arita2016}, this has been exploited to rotate microspheres 
as fast as 1000 Hz while suspended in a bulk medium \cite{Arita2016} as well 
as a means of measuring the local temperature and shear response of said 
medium \cite{Millen2014, RodriguezSevilla2018}. Calculating the optical 
torque applied to a birefringent material is given via:
\begin{equation}
	\label{eq:opt_torque}
	\begin{aligned}
		\tau_{opt} =& -\frac{\epsilon}{2\omega_{laser}}E_0^2sin(kd(\Delta n))cos2\theta sin2\phi 
		\\ &+  \frac{\epsilon}{2\omega_{laser}}E_0^2 (1-cos(kd(\Delta n))sin2\phi)
	\end{aligned}
\end{equation}

Where $\theta$ is the angle between the particle's long axis and the 
polarisation vector of the local EM field, and $\phi$ is the phase shift 
in the EM field. The first term represents the 'orientational' torque which 
is due to the target particle being aligned with the EM amplitude, when 
aligned $\theta=0$ meaning the entire term is negligible for particle's with a stable orientation. For sphere's this is always the case as they lack a 
distinctive major axis. The second term is due purely to the polarisation 
of the optical trap, for circularly polarised light $\phi=\pi/4$ thus 
maximising the torque transferred to the target particle. Eq.~\eqref{eq:opt_torque} is only applicable for particles with a known
birefringence, but there are other mechanisms that result in optical torque.

A common example is shape induced birefringence. If a particle has an 
anisotropic shape, it is more susceptible to being polarised along its 
longer axis than its shorter axis. Consider, for example, an ellipsoid 
elongated along one of its primary axis' ($r_z > r_x = r_y$). In a 
plane polarised beam such a particle will align with the polarisation
vector. Therefore, the particle will rotate as angular momentum is 
transferred along its long axis. The common feature for shape induced
birefringence is that all of these particles are aligned in the plane
of polarisation. Often the optical torque experienced is far greater 
than similar spherical particles that are birefringent. Currently 
spherical dimers are being rotated in vacuums to measure quantum forces
and torques \cite{Ahn2018, Reimann2018}. There are some cases alternative 
cases where particles are rotated while not being aligned in the plane 
of the polarisation. However in these cases their shape is often 
specifically engineered to scatter light either clockwise or 
counter-clockwise \cite{Higurashi1994}.

Other examples of optical torque is when an anisotropic particle is 
aligned with the beam's direction of propagation (in which case $\theta
=\pi/2$ and the first term disappears). This is analogous to an optically trapped sphere, where alongside a restoring force the particle also 
experiences a restoring torque. This seemingly random rotational motion
is referred to as libation \cite{Bruce2020}, often in typical suspension
trapping situations (where the particle is suspended in a fluid) the 
translational motion is washed out by the translational motion. As such, 
many experiments elect to trap in low pressure environments to precisely 
measure the optical torque being exerted by the optical trap \cite{Ahn2018}.
This has lead to experiments to try and achieve '0 kelvin' motion, where
by trapping a silica dimer they were able to restrict its motion using 
3 optical traps simultaneously. Despite this, they found that the dimer's
rotational motion about its long axis could not be controlled leading to
the undesired rotational modes \cite{Bang2020}.

The detection and measurement of optical torque is still a field of intense
research, not only does it have potential to understand quantum fluctuations
in a particle's motion but also allows for the creation of more effective
micro-rotors. The latter being especially pertinent for understanding the 
behaviour of fluids experiencing localised shearing.

\section{Shear induced Nucleation}
It has long been known that fluid shear rate plays a role in influencing
nucleation; however, the exact relationship between shear rate and nucleation
rate has only been recently understood for specific solutions. Theoretical research into shear induced nucleation suggests that there should be a 
slight increase in the nucleation rate at low shear rates, reaching a 
maximum increase in nucleation rate, and then at higher shear rates the 
nucleation rate begins to drop off.

This has been shown theoretically for both simple colloidal \cite{Mura2016,
Debuysschere2023,Richard2015} and ice crystal formation \cite{Goswami2020}; however, no experimental work into these systems has been conducted to prove 
this is the case. There is some experimental evidence for this phenomena in 
simple salt and protein solutions - though the authors emphasise that mechanical agitation cannot be ruled out - there has not been a exhaustive study into the shearing effects apart from in glycine solutions. In \cite{Debuysschere2023} it was found that a shear rate of around $3000\ s^{-1}$ was the maximum shear rate that would yield the highest nucleation rate. Using the theoretical model established in \cite{Mura2016,2001} which modifies the CNT to account for the effects of a nucleus undergoing shearing, 
accounting for the fact that a nucleus' growth is undergoing competition 
between flow-mediated molecular transport and the strain applied by the 
flow field which inhibits the growth of the nucleus. There central 
conclusion (from both the theoretical and experimental results) is that 
there is an optimal shear rate in which the nucleation rate is maximised.

However, a question that arises from this result, if there is a optimal 
shear rate in which molecular transport is maximised and strain is 
minimised, then surely there should also be a shear rate in which the 
molecular transport and strain are equal - allowing one to suspend a 
nucleus at a constant radius. In this scenario, the molecular transport 
would prevent the nucleus from dissolving, but the strain would prevent 
the nucleus from growing. This however would require one to be able 
to apply a continuous shear rate to a targeted nucleus with high precision, there is also no model for an individual nucleus in a continuous fluid 
field.

\section{Significance of Thesis}
As I have hoped to make clear in the above introduction, the current 
state nucleation theory is rather cumbersome at a micro-level. Models
such as CNT and multi-step nucleation are not sufficient for describing
the myriad of potential pathways nucleation can go down. As suggested
by some review articles, the best way to address this is by developing 
\textit{in-situ} methods that can study the pre nucleation phase in 
greater detail \cite{Fu2021}. Furthermore, the ability to localise 
nucleation allows for better characterisation of the kinetics of crystal 
growth. Laser induced nucleation stands to be an ideal method to study
nucleation, as the laser output can be concentrated to a small area. 
In this project we want to consider another application of optical 
tweezers, their ability to rotate micro-rotors to generate fluid flow.
Such a method has not been tried before and would allow for us to 
consider how fluid flow impacts nucleation dynamics at the micro-level.

\section{Overview}
Overall the aim of the PhD is to study viability of using micro-rotors to
generate localised fluid flow around the beam focus. The results are reported
in chapter 3, this is then succeeded by experimental work where we instead 
using a galvano-mirror to generate shear flow. While overall unsuccessful
the addition of a moving beam focus showed that the growth of a nucleus can be localised around the trap focus. This presents a new insights for controlling
and studying the growth of a newly formed nucleus by precise movement of the
trapping focus.

In addition, computer simulations studying the dynamics of asymmetric dimers 
and their applications as complex micro-rotors are discussed in chapter 4. 
The latter results are interesting as a potential insight into how optical
torque is transferred to anisotropic objects.

Lastly two novel methods of measuring rotational motion are discussed in 
chapter 5; firstly via a novel detection fibre method that allows for 
instantaneous measurements of the orientational behaviour of optically 
trapped ellipsoids/dimers; and secondly we create a simulative quadrant 
photo diode that replicates laboratory results, utilising linear regression 
techniques we measure the change in orientation in order to measure the 
optical torque applied to a non-birefringent particle.
